Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-25 analysis/paper/paper.Rmd
combine prep1 and prep2 in one script file, edit code, and knit

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep1-value-burials.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep1-value-burials.R")))
```

>>>>

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep-data.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep-data.R")))
```

### 2021-01-25 analysis/paper/supplementary-material.Rmd
correct variable name and knit
combine prep1 and prep2 in one script file, edit code, and knit

# Introduction to network analysis and archaeological applications

@@

# Kiwulan in the 17th northern Taiwan

@@

# Method

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep1-value-burials.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep1-value-burials.R")))
```

```{r explore-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep2-goods-class-plot.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep2-goods-class-plot.R")))
```

@@

```{r raincloud-beads, fig.cap = "The distributions of different types of trade beads across all burials analyzed in this paper."}
# combine ridge plots 1 & 4 in the 000-prep2 file
library(tidyverse)
library(ggridges)
ridge_1_and_4 <-
  burial_beads %>%
  mutate(type = case_when(
    type == "Golden_bead" ~"gold-foil bead",
    type == "all_glass_bead" ~"glass bead",
    type == "Agate_bead" ~"carnelian bead")) %>% 
  ggplot(aes(x = value,
             y = type,
             fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = 4,
    quantile_lines = TRUE,
    jittered_points = TRUE,
    alpha = 0.7,
    vline_size = 0.5,
    vline_color = "grey10",
    point_size = 2.5,
    point_alpha = 0.4,
    position = position_raincloud(adjust_vlines = TRUE),
    rel_min_height = 0.01,
    scale = 0.5, # so the filled regions don't overlap on the points
    size = 0.2) +
  scale_x_continuous(limits = c(1, 15),
                     expand = c(0.1, 0)) +
  scale_fill_viridis_d(name = "Quartiles") +
  theme_minimal()

@@

# References

>>>>

# Introduction to network analysis and archaeological applications {-}

@@

# Kiwulan in the 17th northern Taiwan {-}

@@

# Method {-}

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep-data.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep-data.R")))
```

@@

```{r raincloud-beads, fig.cap = "The distributions of different types of trade beads across all burials analyzed in this paper."}
# combine ridge plots 1 & 4 in the 000-prep-data file
library(tidyverse)
library(ggridges)
ridge_1_and_4 <-
  burial_beads %>%
  mutate(type = case_when(
    type == "Golden_bead" ~"gold-foil bead",
    type == "all_glass_bead" ~"glass bead",
    type == "Agate_bead" ~"carnelian bead")) %>% 
  ggplot(aes(x = value,
             y = type,
             fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = 4,
    quantile_lines = TRUE,
    jittered_points = TRUE,
    alpha = 0.7,
    vline_size = 0.5,
    vline_color = "grey10",
    point_size = 2.5,
    point_alpha = 0.4,
    position = position_raincloud(adjust_vlines = TRUE),
    rel_min_height = 0.01,
    scale = 0.5, # so the filled regions don't overlap on the points
    size = 0.2) +
  scale_x_continuous(limits = c(1, 15),
                     expand = c(0.1, 0)) +
  scale_fill_viridis_d(name = "Quartiles") +
  theme_minimal()

@@

# References {-}
